Applying Computational Intelligence Methods for Predicting the Sales of Newly Published Books in a Real Editorial Business Management Environment

### 2016-09-08 Response to reviewers.tex

~\\
\noindent (3) \emph{As we known, tree-based methods (e.g., M5P and RF) themselves embed feature selection procedure. That is, some features are chosen to build trees. It is not fair enough to compare five methods in Table 3. }

\begin{verbatim}
Although we agree with the reviewer's comment, and the RF and M5P 
have an embedded feature selection mechanism, we believe that it 
is unfair to compare them with the filter based feature selection 
methods we have deployed in our research. 
The aim is simply to show to the decision maker what are the possible 
results when we apply one of the off-the-shelf classifiers available 
in a common open source framework such as WEKA. 
Moreover, it is not uncommon in the literature to see such comparison 
between classifiers, as in the paper:
  M. Fernandez-Delgado, E. Cernadas, S. Barro, and D. Amorim. 2014. 
  Do we need hundreds of classifiers to solve real world 
  classification problems?. J. Mach. Learn. Res. 15, 1, pp.3133-3181
which incorporates a general comparison between all these classifiers.
\end{verbatim}
%Every response should end with changes made in the paper, even if it
%is only clarification. It is not an invitation to discussion. 
% Antonio - TODO: say how this has been addressed in the paper (where it is clarified). Say if this reference has been included as new.

~\\
\noindent (4) \emph{It seems more reasonable to organize and write that paper according to regression viewpoint only. }

\begin{verbatim}
The reviewer is right, thus, we have revised the whole paper remarking 
the regression topic present on the work. We have clarified in several
 paragraphs that the problem has been addressed by means of regression 
methods (for instance, note the new title of Section 2.1), or we have 
generally referred to the term `regression' instead of `classification', 
in order to better suit the regression viewpoint.
Moreover this suggestion have been also addressed solving the issue 
related to comment #1, where the application procedure of feature 
selection methods for regression problems has been clarified. 
\end{verbatim}

@@

~\\
\noindent (5) \emph{It is necessary to write that paper more concisely. }

\begin{verbatim}
Following reviewer's suggestion we have reorganized some parts 
of the text, removed some sentences, and rewritten several paragraphs 
in order to make them shorter, clearer and to improve its comprehension.

Also, all the tables of results have been moved to the Appendix and 
that data has been presented now as the new Figures XX, YY, ZZ.

@@

Finally, the paper has been completely revised and several 
typographic errors have been fixed.

We are very grateful the reviewer's valuable suggestions and comments. 
\end{verbatim}
% Antonio - TODO: show some examples of reduced text (page/paragraph), there will be some new figures, I think.
% we have to say: "Paragraph #X in subsection #Y" (naming the paragraphs that we identified and gathered-joined)

@@

\begin{verbatim}
Following the reviewer's request, we have conducted several new experiments 
and added the results of ANN (MLP) and ELM to Tables XX, YY, ZZ and
 Figures AA, BB accordingly. 
A description of both approaches have been also included in subsection 2.1.

In addition new references has been added to the paper related to these 
methods, namely [REF_XX, REF_YY].
\end{verbatim}
% Antonio - TODO: Complete with the number of tables and figures, along with the new references
% I don't know what references have been added in this revision. I'll ask Hossam.

~\\
\noindent (2) \emph{The authors should clarify their main contributions in the introduction parts.}

\begin{verbatim}
We have rewritten the introduction and included new paragraphs to better 
explain the problem and the aim of the paper. We have also remarked the
 contribution with the paragraphs:

"Our intention in this paper is to find out the main factors influencing
sales in order to create a tool that the publisher can use to decide how
many books should be printed, as well as how to leverage these printed
copies to maximize sales using the decision variables under his control. 
That is why, using data obtained from a company that sells software for 
publishers, we analyse them and compute predictive models that can be 
mainly used as decision-aid tools for book publishers. With these models,
 publishers will be able to combine their expert knowledge about the market 
with the created forecasting models in order to get a reliable estimation of
 book sales, and, based on it, act consequently in order to maximize the 
books sold for a particular print run. This will improve the current 
decision flow that the publishers follow, which consist in analysing (in a
 subjective way) the quality of the book and its features (author, genre, 
etc), and take a `fuzzy' decision roughly between printing 300 copies 
(standard book) or 5000 (best seller).

Our main contribution is, thus, the development of the methodology 
to process book sales data in order to, first find out relevant variables, 
and then, use these variables to process the data to accurately estimate 
future sales. To our knowledge this is the first work in which regression
 methods have been applied to estimate sales for new launched books. 
Moreover, the use of a real dataset of book sales is another point to 
remark with respect to other works."

Also, in the following paragraphs, we have laid out our 
methodology to differentiate it from other approaches.

\end{verbatim}
% Antonio - TODO: I rewritten this text, so we should copy the new one here. But I think we all should contribute to create a very good justification (see next CONCERN). :D
% Antonio - CONCERN: We should definitely write a convincing text which separates this work from existing approaches. Maybe the use of real data is a good point. And also emphasize the contribution to the SotA.
% [Pedro] well, no previous work on "print run & book sales prediction" has been done (at least, I have not found anything in the bibliography)
% [Hossam] about the contribution, I agree with you. We can mention that we used real data in our work.

@@

~\\
\noindent (3) \emph{Technologies related to recommend systems may have the ability to deal with this problem. The authors should add the recommend systems into the future work part. }

\begin{verbatim}
Taking into account the reviewer's comment, the recommendation 
systems have been added to the future work section, at the end 
of Section 7 (see page XX).
\end{verbatim}
% Antonio - TODO: put the correct page when the text is finished

~\\
\noindent (4) \emph{Some tables should be transfer to figures because there are too many tables. }

\begin{verbatim}
Following reviewer's suggestion, all the results tables have been 
moved to the Appendix and that data has been summarized and 
presented as the new Figures XX, YY, ZZ in order to make that numeric 
data clearer and to improve their comprehension.
\end{verbatim}
% Antonio - TODO: put the correct page when the text is finished

@@

\noindent \emph{There are several concerns should be considered.}\\

\noindent (1) \emph{In section introduction, this manuscript should describe the contribution of this work. }

\begin{verbatim}

The reviewer is right. The main contribution of this paper to the 
state of the art was not properly described. Thus, as stated above 
in the second response to Reviewer #2, we have clarified this in 
the introduction adding new sentences and the paragraph:

"Our main contribution is, thus, the development of the methodology 
to process book sales data in order to, first find out relevant variables, 
and then, use these variables to process the data to accurately estimate 
future sales. To our knowledge this is the first work in which regression
 methods have been applied to estimate sales for new launched books. 
Moreover, the use of a real dataset of book sales is another point to 
remark with respect to other works."

\end{verbatim}
% Antonio - TODO - put here the paragraph as it will finally be (if it is changed again).

@@

~\\
\noindent (3) \emph{In section 4, this manuscript should show a flowchart of the proposed forecasting scheme and describe it. }

\begin{verbatim}
Taking into account the reviewer's comment, we have improved the 
description of the methodology including a flowchart (see Figure XX 
at page YY).
\end{verbatim}
% Antonio - CONCERN: I don't know if te reviewer is speaking about the whole methodology or just about the regression/forecasting part... The figure shows a rough summary of the methodology.
% Antonio - TODO: Improve the figure, which is a bit 'generic'. Put the correct figure and page.
% Almost every paper I have read (and that has been cited in the SotA) shows a very generic flowchat

~\\
\noindent (4) \emph{In Section 5, parameter settings of 
M5P, kNN and RF also should be shown. }

\begin{verbatim}
Reviewer is right, so we have improved Section 5, including the 
parameter settings of M5P, kNN and RF methods (see paragraph XX at 
page YY), along with the configuration parameters for the rest of 
methods.

### 2016-09-08 paper.tex
all tables of results in the appendix: Closes #53
Let's finish the graphical abstract  ;)  Closes #51
the appendix is now in one column format (the section title too)
Working on the paper: Sections 1-4
Intro, SotA, Problem, Methodology.

Responses to reviewers improved.

In general, forecasting the sales of cultural products can
only be based on the knowledge obtained from sales of other, similar, ones,
but the definition of ``similar'' itself is fuzzy and, sometimes,
subjective. Even if the author or the topic is known, making accurate
estimations of future sales of the new product is quite difficult, and
extremely important, so that production runs follow predicted sales.  
Indeed, several studies have demonstrated that improving sales
predictions, that is reducing the error in estimated sales, results in an enhancement in the 
production process \cite{Fildes2010,Saeed2008}, so not only cost
associated to the book itself are associated,
% (Paloma) I was about to change this second "associated" for "affected" (seems the right thing to do). However, what's after this comma is also confusing, given that we already said that is affects to the whole production process. Maybe who wrote this should re-think what he/she meant to say here and change it.
 but also the whole
production process.

Within the general area of cultural products, the problem of
predicting sales is specially acute for book publishers who, among other
providers of content in physical form, release new {\em products} more frequently than
other industries, so that they face the problem of predicting sales quite often. The issue, in this case, is to print an adequate number of copies but not too many, as the unsold volumes will lead to losses and sunk inventory cost, 
whereas if the number of printed copies was not enough, a new print
run can always be made, resulting in temporary losses due to a lack of supply
or in bad marketing for the customers, for instance. However, in
practice predicting lower sales than the actual ones is not such a big
problem because when inventory is close to exhaustion new print runs
are made; % (Paloma) I think that the thing that should be highlighted here is that is not big deal because the print run is made _before_ the inventory is exhausted. I mean, the sentence highlights the fact that a new print run is made, and not that maybe the situation where there's any book never happens. 
% Suggestion:  However, in practice predicting lower sales than the actual ones is not such a big problem because the new print run is orderer before the inventory is exhausted;
 nevertheless, this new print run presents the same problem as the
initial one of printing only as many as forecasted, although its cost
is not as high as the initial one 
% (Paloma) Should we really say this next sentence? :\
and we are not so concerned with
this issue in this paper.

@@

% I don't know what to make with this paragraph. Move it to the
% presentation of the problem, move it to the state of the art, or
% eliminate it completely. Whoever wrote it please help - JJ
It is important to notice that the accuracy of the predictive method
that we intend to design is affected negatively by several factors
related to decisions on purchases, to freight traffic, or with the
distribution strategy \cite{Little1998}. 
Thus, it is mandatory to know the product and the variables that
might affect the sales, and how an expert manager takes them into 
account \cite{Armstrong2001,SThomassey2014}. 
Moreover, their impact is difficult to estimate and it is not constant over time, hence the complexity to adequately identify and measure their influence \cite{DeToni2000}.
In addition, some variables may have correlations between them, although these correlations can be detected using data analysis methods, 
such as Self-Organizing Maps (SOM) \cite{kohonen1998} or stepwise regression analysis (SRA) \cite{Chang2009}.

In Spain, the process of releasing a book goes like this: the
publisher decides, based on past experience, how many books to
print. These books are distributed to points of sale, but also given
out to reviewers and literary magazines; the number of these will
depend on how many you have printed. In bookstores books  go, in some cases, to
the {\em novelty} table, that is, they are prominently displayed, shown in the window, or highlighted using props or other 
kind of advertisement. From these displays they then move to shelves
or, in some cases and eventually, to storage. Books stay for sale in the store as long as the
publisher or the store want or until the bookseller decides to return it
to the publisher. Books returned to the publisher are pulped, sold back or
given to the author or distributed in used-books channels such as
book stalls or second-hand bookstores. If the print run has been fully
distributed and there are more requests from bookstores, on the other
hand, a new print run is made and distributed to bookstores. 
Even if the process has changed slightly 
in the last few years since Amazon started to sell in Spain, in the
sense that many books are sold through this new channel and do not
undergo the cycle novelty table-shelf-storage-back to publisher, which
actually happened {\em after} the data used for this paper was
collected, it roughly stays the same. Other countries will have a
similar model, although scale will be different.

@@

Our main contribution is, thus, the development of the methodology to process book sales data in order to, first find out
relevant variables, and then, use these variables to process the data to accurately estimate future sales.

In the research published in this paper, the problem of predicting total sales is approached using real data provided by the 
Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}}. This company offers management systems and services for bookshops, publishers, and distributors. 
Usually, the company's expert sales managers analysed historical data
and applied their knowledge on external variables to compute correct
estimations (predictions); for instance, they can decide increasing or
decreasing the sales forecast based on season or sales period. 
Nevertheless, just carrying out the analysis and forecasting process
as a human expert may lead to imprecise predictions, and they may not
take all the variables into account.  
In addition, the process might be tedious, especially when the amount
of data is quite large. Moreover, different experts can reach different
predictions from the same dataset \cite{Sanders1994}.

%An initial version of this method was developed under a contract with that company and eventually integrated in their product. This paper represents an improved version of that method based on the same data. 
% We should also mention what data we actually mean, I don't think
% we've published it here. - JJ
% Antonio - I think this information is not relevant for the paper...

@@

The rest of this paper is structured as follows: next, Section \ref{sec:soa} presents a comprehensive review of the approaches found in the bibliography related to sales prediction in similar scopes. 
Then, Section \ref{sec:problem} introduces the problem of the estimation of print-run for new books, along with a description of the considered dataset.
Section \ref{sec:methodology} details the methodology considered in the study, from the data collection and preprocessing stages, to the selection of the forecasting methods to be applied in the experiments.  These are reported in Section \ref{sec:experiments}, which is also devoted to analyse the obtained results in feature selection and book sales forecasting using different datasets, with different amounts of features, for all the publishing companies. Obtained results for the four considered special cases are commented in Section \ref{sec:example_cases}. Finally, conclusions and future lines of work are presented in Section \ref{sec:conclusionsAndFutureWork}.

@@

  %[pedro] sobre la industria editorial no hay trabajos sobre predicción de ventas.
  % Lo habitual ha sido usar el conocimiento de expertos para realizar predicciones 
  %  o aconsejar acerca de la cantidad de libros a imprimir.
  % Lo más parecido que he encontrado son dos trabajos (uno en realidad) de Moon et al. 
  %  sobre "Use Blog Information As Book Sales Prediction":
  %     Moon2010ICSSSM , Moon2010ICEC
Recently, some works have proposed analysing relationships between on-line 
information and book sales \cite{Moon2010ICSSSM,Moon2010ICEC}. 
Specifically, Moon et al. propose using the number of blog references as an 
indicator of the success of a book, and thus, its sales. 
Obtained results confirm relationships between the number of blog references 
and book sales, and at the same time different sales patterns are observed 
by analysing books in series (the first book published takes the longest period 
to achieve every single sales scale, while the second book takes the second 
longest period, and so on).

%
% pasar a contar los casos de la predicción de ventas en la 
% industria de la moda (SThomassey2014) y de nuevos productos (ChingChin2010)
%
% Son problemas muy similares, ya que no hay datos históricos de los nuevos productos,
% al igual que no los hay sobre ventas, y en los que además influyen mucho las variables 
% externas (estacionalidad, modas, fama del author, etc).
% Hay que echar mano de productos similares o simplemente de los datos que describen el nuevo producto.
%

@@

The complexity of this problem relies on the lack of historical data, on the 
short lifetime of the majority of items, and on the influence of variables such 
as promotions, fashions, or economic environment
 \cite{Thomassey2012,Xia2012,SThomassey2014}, as mentioned above.
%FERGU: completar con: "In our case, these ideas ..."
% [pedro] no sé a qué te refieres. Please, detalla un poco esto   :)

  %[Pedro] otro caso muy similar es el paper de ChingChin2010 sobre:
  % New tea product
  % New cosmetic product
  % New soft drink product
Ching et al. propose in \cite{ChingChin2010} a decision-support system for new 
product sales forecasting to solve three real-world sales forecasting 
problems, namely: new tea, cosmetics, and soft drink products. 
In that study, products are classified based on their sales patterns, so it is 
assumed that products in the same class would follow a similar sales pattern. 
However, as the authors state, the proposed system can not deal with qualitative 
data related to the products. Moreover, real-world cases, such as consumer 
electronics and fashion products, should be deeply analysed, as these industries 
present/launch new products every season.

  %[Pedro] otro caso a comentar es el paper de Chang2009 sobre: 
  % sales forecasting in printed circuit board industry.
On the other hand, in those cases where historical data are available, classical time series forecasting methods have been applied, such as in \cite{Chang2009}, 
where a hybrid model integrating K-Means and fuzzy neural networks to forecast 
the future sales of a printed circuit board is proposed.
A similar method is described by Chern et al. \cite{ChernWSF15}, who analysed 
historical data throughout online reviews, reviewer characteristics, and review 
influences to understand how electronic `word-of-mouth' influences product sales. 
In this case, the proposed method is suitable for those sales forecasting problems 
with a big amount of online reviews and historical data.

@@

Many of the previous papers propose using different prediction methods.
Thus, next subsections describe several forecasting methods and different 
evaluation metrics, commonly used in the bibliography that have been chosen 
to face the problem at hand.

@@

 % weka.classifiers.lazy.IBk 
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/lazy/IBk.html
 \item \emph{k-Nearest Neighbours (kNN)}: 
The kNN \cite{Aha1991,Mitchell1997} method is an instance-based classifier in 
which the unknown instances are classified by relating them to the known 
instances using a distance measurement/function: Euclidean, Minkowsky or minimax.
% Antonio - CONCERN - should we change the term 'classification' by 'regression' somehow?
% I don't think so in this case. That is what kNN is...

@@

%In classification problems the algorithm searches for an optimal hyperplane 
%that separates two classes, maximising the margin between them.
% Antonio - CONCERN - remove this classification thing due to a reviewer's comment 
% ok    :)
In regression problems, the algorithm chooses a hyperplane close to as many 
of the data points as possible, minimising the sum of the distances from 
the data points to the hyperplane. 
In both cases, the hyperplane is defined by a subset of training set samples, 
called support vectors.
%This method works well even if the space is highly dimensional and the problem is not linearly separable.

 % weka.classifiers.functions.MultilayerPerceptron
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/MultilayerPerceptron.html
 \item \emph{Multilayer Perceptron}:
A Multilayer Perceptron (MLP) \cite{Rosenblatt1962,Widrow1990} is a feedforward 
artificial neural network model that maps the input data onto an appropriate output. 
It is an artificial neural network generally used for classification or 
approximation problems.
% Antonio - CONCERN - something about regression?
% in that sentence, approximation is used as synonymous of regression   ;)

@@

\item \emph{Extreme learning machine (ELM)}: 
ELM is an algorithm for training a single hidden 
layer feedforward neural network which was first proposed by Guang-Bin Huang \cite
{huang2006extreme}. A typical implementation of ELM is a single hidden layer network where the 
connection weights between the input layer and the hidden layer are randomly initialized and 
fixed, while the connection weights between the hidden layer the output layer are learned 
analytically in a single step of linear parameters solving. In ELM the hidden layer maps the 
input data into a feature space called ELM feature space using non-linear activation functions 
such as Sigmoid, Hyperbolic and Gaussian functions \cite{huang2015trends}.The main advantages 
of ELM are the ease of use and the very efficient learning speed compared to other traditional 
training methods such as the Backpropagation algorithm.

@@

The objective is finding the most appropriate forecasting method that minimises 
the error between the obtained forecast and the current sales for each new book 
published.

% Antonio - TODO: link this section with the rest of the SotA. Introduce it in a paragraph before. And rewrite the initial paragraphs to separate it from section 4 (methodology)
% I have addressed this "todo" before (lin. 353)

@@

At this step, the developed forecasting models are evaluated and assessed based on different evaluation criteria. In addition to the \textit{correlation coefficient}, we have considered the widely accepted standard formulae in the literature \cite{gepsoft} (Equations \ref{eq:MAE} to \ref{eq:RRSE}), which are implemented in tools like Weka \cite{pentaho,Witten2011} or R \cite{otexts,Hyndman2013}.
Specifically, in order to compute the forecasting errors of the different methods, Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute error (RAE) and Root relative squared error (RRSE) have been selected:

@@

% previous two sub-sections have been moved here as requested by reviewer #3 in comment #2 (issue #47)
% Antonio - TODO - revise them
% What have to be revised?   :/

@@

Starting from these raw data, a preprocessing method has been performed in order to remove incorrect or incoherent patterns, such as those with null values in required variables, or with negative sales, for instance. 
% (Paloma) Why remove those with null values and not to use an algorithm to fill those missing values?
% Antonio - because we should not fill important variables automatically, this adds noise to the data, so I think it is better to remove these patterns, since there are still a lot in the dataset. 
% Indeed, there were just a couple of patterns without important values, that probably were errors of the extraction process or bad insertions in the database.
Furthermore, the initial set of variables, presented in Table \ref{tabla:paramsOrig50}, 
has been reduced by an expert to use just those that can be known before a new book 
is launched, i.e. \textit{pre-sales data}. 
%Thus, their value do not depend on the book sales. 
The selected subset of features is described in Table \ref{tabla:params_pre_sales}.

@@

In this prediction problem there are other external variables that also affect 
the sales of a new book, such as those related to seasonality, trends, or 
promotions, that classical prediction methods can not deal with, since they 
are not included in the dataset due to the difficulty to model them. 
However, an expert can consider them to modify the forecast obtained by 
the automatic method. Even publishing companies tend to define rules or 
indexes to subjectively adjust the results of prediction based on
external data. 
Thus, the proposed method will analyse the provided data and
variables and will yield a forecast of sales according to them. This
result could be used as a reference for a human expert, who would
consider it for his or her own prediction process.

% This section is too short and really does not describe the problem
% to its full extent. First, it should say if some of these variables
% were discarded for some reason. Group the variables we have in those
% available to publisher and those that can be used afterwards. And
% then give an idea of the complexity of the problem and how difficult
% it should be to find a solution - JJ
% Antonio - I have included much more contents form other sections. could you do the rest?

% You should include data visualization in problem description,
% because it shows the distribution of problem variables and then
% suggests ways to deal with it - JJ
% You should include in the section an exploratory data
% analysis that describes the range of variables, how many categories
% those variables have, and so an do forth - JJ
% Antonio - as you know SOM has been applied later as a feature selection method... I don't know if we could reference the figure of SOM here or the other way round (do the analysis here and reference later), but in that case, we should explain SOM before, which could be a mess...
% Antonio - If you meant using other visualization methods... could you do it also?

@@

\begin{figure}[!h] 
\begin{center}
  \epsfig{file=metodologia.eps,width=5.5cm}
\caption{Steps followed in the proposed methodology.}
\label{fig:methodology}
\end{center}
\end{figure}

@@

In this stage, both numerical and visualisation-based approaches have been 
applied, in order to select the best variables for the forecasting methods.  
% Antonio - Should we speak about 'forecasting' or 'regression', Sam? Could they be used with the same meaning?
% I think so.

As stated before, in Section \ref{subsec:select_method}, a selection of the best 
forecasting techniques has been reported, looking for those rule- or tree-based, 
together with numerical regression methods which could yield the best results.

Once the models and results have been obtained for the whole dataset 
(Section \ref{sec:experiments}), the same methodology has been applied to some 
specific cases of publishing companies in order to prove the value of the 
proposal (Section \ref{sec:example_cases}).
Some specific interpretable models have been created as a final result of the work.

@@

% Why? Is that one of the two forms of feature selection? What do we expect to learn from it? - JJ 
% Antonio - explained here and below. Please check.

%--- new SOM description % -Sam

@@

% Antonio - a better description of U-Matrix. ;D
% thanks!

@@

Finally, Section \ref{sec:experiments} provides a comparison between 
the feature reduction through SOM, and the feature selection techniques 
that have been described.

>>>>

In general, forecasting the sales of cultural products can
only be based on the knowledge obtained from sales of other, similar, ones,
but the definition of ``similar'' itself is fuzzy and, sometimes,
subjective. Even if the author or the topic is known, making accurate
estimations of future sales of the new product is quite difficult, and
extremely important, so that production runs follow predicted sales.  
Indeed, several studies have demonstrated that improving sales
predictions, that is reducing the error in estimated sales, results in an enhancement in the whole production process \cite{Fildes2010,Saeed2008}, so not only the costs associated to the book itself are affected.
% (Paloma) I was about to change this second "associated" for "affected" (seems the right thing to do). However, what's after this comma is also confusing, given that we already said that is affects to the whole production process. Maybe who wrote this should re-think what he/she meant to say here and change it.
% Antonio - I guess it was a mistake. I think now it is correct.

Within the general area of cultural products, the problem of
predicting sales is specially acute for book publishers who, among other
providers of content in physical form, release new {\em products} more frequently than
other industries, so that they face the problem of predicting sales quite often. The issue, in this case, is to print an adequate number of copies but not too many, as the unsold volumes will lead to losses and sunk inventory cost, 
whereas if the number of printed copies was not enough, a new print
run can always be made, but this will result in temporary losses due to a lack of supply or in bad marketing for the customers, for instance. However, in practice predicting lower sales than the actual ones is not such a big problem because the new print run is ordered before the inventory is exhausted; 
% (Paloma) I think that the thing that should be highlighted here is that is not big deal because the print run is made _before_ the inventory is exhausted. I mean, the sentence highlights the fact that a new print run is made, and not that maybe the situation where there's any book never happens. 
% Suggestion:  However, in practice predicting lower sales than the actual ones is not such a big problem because the new print run is orderer before the inventory is exhausted;
% Antonio - fixed then
 nevertheless, this new print run presents the same problem as the
initial one of printing only as many as forecasted, although its cost
is not as high as the initial one. 
% (Paloma) Should we really say this next sentence? :\
%and we are not so concerned with
%this issue in this paper.
% Antonio - yes, no need to say this

@@

In Spain, the process of releasing a book goes like this: the
publisher decides, based on past experience, how many books to
print. These books are distributed to points of sale, but also given
out to reviewers and literary magazines; the number of these will
depend on how many you have printed. In bookstores books go, in some cases, to
the {\em novelty} table, that is, they are prominently displayed, shown in the window, or highlighted using props or other 
kind of advertisement. From these displays they then move to shelves
or, in some cases and eventually, to storage. Books stay for sale in the store as long as the
publisher or the store want or until the bookseller decides to return it
to the publisher. Books returned to the publisher are pulped, sold back or
given to the author, or finally distributed in used-books channels such as
book stalls or second-hand bookstores. If the print run has been fully
distributed and there are more requests from bookstores, on the other
hand, a new print run is made and distributed to these shops. 
Even if the process has changed slightly 
in the last few years since Amazon started to sell in Spain, in the
sense that many books are sold through this new channel and do not
undergo the cycle novelty table-shelf-storage-back to publisher, which
actually happened {\em after} the data used for this paper was
collected, it roughly stays the same. Other countries will have a
similar model, although the scale will be different.

@@

Our main contribution is, thus, the development of the methodology to process book sales data in order to, first find out relevant variables, and then, use these variables to process the data to accurately estimate future sales. To our knowledge this is the first work in which regression methods have been applied to estimate sales for new launched books. Moreover, the use of a real dataset of book sales is another point to remark with respect to other works.

Therefore, in this paper, the problem of predicting total sales is approached using real data provided by the Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}}. This company offers management systems and services for bookshops, publishers, and distributors. 
Usually, the company's expert sales managers analysed historical data
and applied their knowledge on external variables to compute correct
estimations (predictions); for instance, they can decide increasing or
decreasing the sales forecast based on season or sales period. 
Nevertheless, just carrying out the analysis and forecasting process
as a human expert may lead to imprecise predictions, and they may not
take all the variables into account.  
In addition, the process might be tedious, especially when the amount
of data is quite large. Moreover, different experts can reach different
predictions from the same dataset \cite{Sanders1994}.

@@

The rest of this paper is structured as follows: next, Section \ref{sec:soa} presents a comprehensive review of the approaches found in the bibliography related to sales prediction in similar scopes and shows a set of definitions of the regression methods applied in the paper and the evaluation metrics considered.
Then, Section \ref{sec:problem} introduces the problem of the estimation of print-run for new books, along with a description of the considered dataset.
Section \ref{sec:methodology} details the methodology considered in the study.  These are reported in Section \ref{sec:experiments}, which is also devoted to analyse the obtained results in feature selection and book sales forecasting using different datasets, with different amounts of features, for all the publishing companies. Obtained results for the four considered special cases are commented in Section \ref{sec:example_cases}. Finally, conclusions and future lines of work are presented in Section \ref{sec:conclusionsAndFutureWork}.

@@

Recently, some works have proposed analysing relationships between on-line 
information and book sales \cite{Moon2010ICSSSM,Moon2010ICEC}. 
Specifically, Moon et al. propose using the number of blog references as an 
indicator of the success of a book, and thus, its sales. 
Obtained results confirm relationships between the number of blog references 
and book sales, and at the same time different sales patterns are observed 
by analysing books in series (the first book published takes the longest period 
to achieve every single sales scale, while the second book takes the second 
longest period, and so on).

@@

The complexity of this problem relies on the lack of historical data, on the 
short lifetime of the majority of items, and on the influence of variables such 
as promotions, fashions, or economic environment
 \cite{Thomassey2012,Xia2012,SThomassey2014}, as mentioned above.

Ching et al. propose in \cite{ChingChin2010} a decision-support system for new 
product sales forecasting to solve three real-world sales forecasting 
problems, namely: new tea, cosmetics, and soft drink products. 
In that study, products are classified based on their sales patterns, so it is 
assumed that products in the same class would follow a similar sales pattern. 
However, as the authors state, the proposed system can not deal with qualitative 
data related to the products. Moreover, real-world cases, such as consumer 
electronics and fashion products, should be deeply analysed, as these industries 
present/launch new products every season.

On the other hand, in those cases where historical data are available, classical time series forecasting methods have been applied, such as in \cite{Chang2009}, 
where a hybrid model integrating K-Means and fuzzy neural networks to forecast 
the future sales of a printed circuit board is proposed.
A similar method is described by Chern et al. \cite{ChernWSF15}, who analysed 
historical data throughout online reviews, reviewer characteristics, and review 
influences to understand how electronic `word-of-mouth' influences product sales. 
In this case, the proposed method is suitable for those sales forecasting problems with a big amount of online reviews and historical data.

@@

Many of these previous papers propose using different prediction methods to find out which one performs the best.
Thus, next subsections describe several forecasting methods and different 
evaluation metrics, commonly used in the bibliography that have been chosen 
to address the problem of book sales prediction.

@@

 % weka.classifiers.lazy.IBk 
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/lazy/IBk.html
 \item \emph{k-Nearest Neighbours (kNN)}: 
The kNN \cite{Aha1991,Mitchell1997} method is an instance-based classifier in 
which the unknown instances are classified by relating them to the known 
instances using a distance measurement/function: Euclidean, Minkowsky or minimax.

@@

In regression problems, the algorithm chooses a hyperplane close to as many 
of the data points as possible, minimising the sum of the distances from 
the data points to the hyperplane. 
In both cases, the hyperplane is defined by a subset of training set samples, 
called support vectors.
%This method works well even if the space is highly dimensional and the problem is not linearly separable.

 % weka.classifiers.functions.MultilayerPerceptron
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/MultilayerPerceptron.html
 \item \emph{Multilayer Perceptron}:
A Multilayer Perceptron (MLP) \cite{Rosenblatt1962,Widrow1990} is a feedforward 
artificial neural network model that maps the input data onto an appropriate output. 
It is an artificial neural network generally used for classification or 
approximation/regression problems.

@@

\item \emph{Extreme learning machine (ELM)}: 
ELM is an algorithm for training a single hidden 
layer feedforward neural network which was first proposed by Guang-Bin Huang \cite
{huang2006extreme}. A typical implementation of ELM is a single hidden layer network where the 
connection weights between the input layer and the hidden layer are randomly initialized and 
fixed, while the connection weights between the hidden layer the output layer are learnt 
analytically in a single step of linear parameters solving. In ELM the hidden layer maps the 
input data into a feature space called ELM feature space using non-linear activation functions 
such as Sigmoid, Hyperbolic and Gaussian functions \cite{huang2015trends}.The main advantages 
of ELM are the ease of use and the very efficient learning speed compared to other traditional 
training methods such as the Backpropagation algorithm.

@@

The objective is finding the most appropriate forecasting method that minimises 
the error between the obtained forecast and the current sales for each new book 
published. To this end, the results will be evaluated using different metrics, as described in the following section.

% Antonio - I have linked the section also here for a more fluent reading. ;)

@@

The developed forecasting models must be evaluated and assessed based on different evaluation criteria. In addition to the \textit{correlation coefficient}, we have considered the widely accepted standard formulae in the literature \cite{gepsoft} (Equations \ref{eq:MAE} to \ref{eq:RRSE}), which are implemented in tools like Weka \cite{pentaho,Witten2011} or R \cite{otexts,Hyndman2013}.
Specifically, in order to compute the forecasting errors of the different methods, Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute error (RAE) and Root relative squared error (RRSE) have been selected:

@@

@@

Starting from these raw data, a preprocessing method has been performed in order to remove incorrect or incoherent patterns, such as those with null values in required variables, or with negative sales, for instance. 
Furthermore, the initial set of variables, presented in Table \ref{tabla:paramsOrig50}, has been reduced by an expert to use just those that can be known before a new book is launched, i.e. \textit{pre-sales data}. 
%Thus, their value do not depend on the book sales. 
The selected subset of features is described in Table \ref{tabla:params_pre_sales}.

@@

In this prediction problem there are other external variables that also affect 
the sales of a new book \cite{Little1998}, such as those related to seasonality, trends, or promotions, that classical prediction methods can not deal with, since they are not included in the dataset due to the difficulty to model them. 
However, an expert can consider them to modify the forecast obtained by 
the automatic method \cite{Armstrong2001}. Even publishing companies tend to define rules or  indexes to subjectively adjust the results of prediction based on external data. 
Thus, the proposed method will analyse the provided data and
variables and will yield a forecast of sales according to them. This
result could be used as a reference for a human expert, who would
consider it for his or her own prediction process.

@@

\begin{figure}[!ht] 
\begin{center}
  \epsfig{file=metodologia.eps,width=5.5cm}
\caption{Steps followed in the proposed methodology.}
\label{fig:methodology}
\end{center}
\end{figure}

@@

In this stage, both numerical and visualisation-based approaches have been 
applied, in order to select the best variables for the forecasting methods.  
The methods to apply are those described in Section \ref{subsec:select_method},  which include rule- and tree-based algorithms, together with numerical regression methods.

The obtained models for the whole dataset have been evaluated by means of the metrics described in Section \ref{subsec:models_evaluation}. The results are presented in Section \ref{sec:experiments}. Then, the same methodology has been applied to some specific cases of publishing companies in order to prove the value of the proposal (Section \ref{sec:example_cases}).
Specific interpretable models have been created as a final result of the work (Section \ref{subsec:decision_trees}).

% Antonio - CONCERN - The following section seems to be bad placed now. The Methodology Section is now a bit strange with just this subsection. We should think on moving this section and reorganize/improve the methodology description.

@@

@@

@@

Next section provides a comparison between the feature reduction through SOM, and the feature selection techniques that have been described.
